PYTHON CONVERSION README BSP3 project\+: Computational Tools for Music Python Conversion

This Readme file concerns the python translated version of a java project about the musical structures discussed by Luigi Verdi in his book \char`\"{}\+Caleidocicli Musicali\char`\"{}. This project was developped by a student at the University of Luxmebourg under the supervision of M.\+di Tollo. To understand all the key terms of the project, please refer to the BSP report written alongside the code.

PLEASE NOTICE that this software has been developed to be used on Windows and portability is not guaranteed.

Required language\+: Python 3.\+10.\+0 Installation process\+: Follow the link \href{https://www.python.org/downloads/}{\texttt{ https\+://www.\+python.\+org/downloads/}} and select the version 3.\+10.\+0 for the OS that you are using. Since this project was developped on Windows 10 so using this OS is recommended. Once the download started, follow the instrcutions given on the installer. For additional information for Windows follow this link\+: \href{https://phoenixnap.com/kb/how-to-install-python-3-windows}{\texttt{ https\+://phoenixnap.\+com/kb/how-\/to-\/install-\/python-\/3-\/windows}} To install on Linux, follow this link\+: \href{https://opensource.com/article/20/4/install-python-linux}{\texttt{ https\+://opensource.\+com/article/20/4/install-\/python-\/linux}} To install on Mac OS, follow this link\+: \href{https://www.freecodecamp.org/news/python-version-on-mac-update/}{\texttt{ https\+://www.\+freecodecamp.\+org/news/python-\/version-\/on-\/mac-\/update/}}

Required libraries\+: Pip, Py\+Qt5, Qt Designer, pyqtgraph Installation processes for Windows\+: Pip\+: Pip is a package manage for python. Make sure python is installed before continuing. The main documentation is found here\+: \href{https://pypi.org/project/pip/}{\texttt{ https\+://pypi.\+org/project/pip/}} Installation process is found here\+: \href{https://phoenixnap.com/kb/install-pip-windows}{\texttt{ https\+://phoenixnap.\+com/kb/install-\/pip-\/windows}}

Py\+Qt5\+: The Py\+Qt5 is a module that is used to create desktop applications in python. Make sure pip is installed before continuing. The installation process is found here\+: \href{https://pythonbasics.org/install-pyqt/}{\texttt{ https\+://pythonbasics.\+org/install-\/pyqt/}}

Qt Designer\+: Qt Designer is used to make the Py\+Qt5 application designing process easier. Make sure Py\+Qt5 is installed before continuing. The installation process is found here\+: \href{https://build-system.fman.io/qt-designer-download}{\texttt{ https\+://build-\/system.\+fman.\+io/qt-\/designer-\/download}}

pyqtgraph\+: pyqtgraph is used to design graphs for the visual representations The installation process is found here\+: \href{https://pyqtgraph.readthedocs.io/en/latest/installation.html}{\texttt{ https\+://pyqtgraph.\+readthedocs.\+io/en/latest/installation.\+html}}

HOW TO RUN THE PROGRAM\+: Make sure you are in the correct path\+: ...\textbackslash{}\+LUIGIVERDI\textbackslash{}\+Proj3\+\_\+\+Python\+Convertion To run the code in the terminal use the command\+: python main.\+py Three questions will appear and ask the different parameters. If the parameters entered are not valid, the code will not run. There are 5 tabs\+: -\/the first one gives general information about the cycle, the two kaleidos and the two kaleidocycles -\/the four other tabs are the visual representation of the objects mentionned above The user can zoom in/out as well as scoll to the sides on the graphs, but this is not necessary since the graphs are scaled automatically to see all the points in the window. 